---
title: "Combine_Seurat_CryptoInfection"
author: "AndrewHart"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

##Load the Libraries----
```{r, warning=FALSE, error=FALSE}
library(Seurat)
library(Signac)
library(dplyr)
library(ggplot2)
library(reshape2)
library(data.table)
library(cowplot)
library(scCustomize)
library(forcats)
library(ggbreak)
library(presto)
library(ggforce)
library(SingleR)
library(celldex)
library(harmony)
library(Azimuth)
library(glmGamPoi)
library(future)
library(dsb)
library(RColorBrewer)


#options(future.globals.maxSize = 2000 * 1024^2)
```


```{r setup}
setwd("/data/hartandrew/MIST/SingleCell")
```
#Load Samples - Mouse




#Load Samples - Negative Control Crypto Alignment
#CHMI24134_MLN_crypto
```{r}
raw.data <- Read10X(data.dir = "/data/hartandrew/CellRanger/CHMI_192/MIST24134_MLN_crypto/outs/raw_feature_bc_matrix/")
filtered.data <- Read10X(data.dir = "/data/hartandrew/CellRanger/CHMI_192/MIST24134_MLN_crypto/outs/filtered_feature_bc_matrix/")
rownames(x = filtered.data[["Antibody Capture"]]) 
crypto_CHMI24134_MLN <- CreateSeuratObject(counts = filtered.data, project = "crypto_")

FeatureScatter(crypto_CHMI24134_MLN, "nCount_RNA", "nFeature_RNA", pt.size = 0.5)
VlnPlot(crypto_CHMI24134_MLN, features = c("nCount_RNA"), pt.size = 0.1) + ylim(0,12000)

VlnPlot(crypto_CHMI24134_MLN, features = c("nFeature_RNA"), pt.size = 0.1) + ylim(0,500)

crypto_CHMI24134_MLN <- subset(crypto_CHMI24134_MLN, subset =
                             nFeature_RNA > 150 &
                              nCount_RNA > 500)
length(crypto_CHMI24134_MLN$orig.ident)

```



#Load Samples - Positive Control Crypto Alignment
#CHMI2489_LP_crypto
```{r}
raw.data <- Read10X(data.dir = "/data/hartandrew/CellRanger/CHMI_183/MIST2489_LP_crypto/outs/raw_feature_bc_matrix/")
filtered.data <- Read10X(data.dir = "/data/hartandrew/CellRanger/CHMI_183/MIST2489_LP_crypto/outs/filtered_feature_bc_matrix/")
rownames(x = filtered.data[["Antibody Capture"]]) 
crypto_CHMI2489_LP <- CreateSeuratObject(counts = filtered.data, project = "crypto_")

FeatureScatter(crypto_CHMI2489_LP, "nCount_RNA", "nFeature_RNA", pt.size = 0.5)
VlnPlot(crypto_CHMI2489_LP, features = c("nCount_RNA"), pt.size = 0.1) + ylim(0,12000)

VlnPlot(crypto_CHMI2489_LP, features = c("nFeature_RNA"), pt.size = 0.1) + ylim(0,1000)

length(crypto_CHMI2489_LP$orig.ident)

crypto_CHMI2489_LP <- subset(crypto_CHMI2489_LP, 
                             nFeature_RNA > 150 
                             & nCount_RNA > 250)

```




#CHMI2489_IEL_crypto
```{r}
raw.data <- Read10X(data.dir = "/data/hartandrew/CellRanger/CHMI_183/MIST2489_IEL_crypto/outs/raw_feature_bc_matrix/")
filtered.data <- Read10X(data.dir = "/data/hartandrew/CellRanger/CHMI_183/MIST2489_IEL_crypto/outs/filtered_feature_bc_matrix/")
rownames(x = filtered.data[["Antibody Capture"]]) 
crypto_CHMI2489_IEL <- CreateSeuratObject(counts = filtered.data, project = "crypto_")

FeatureScatter(crypto_CHMI2489_IEL, "nCount_RNA", "nFeature_RNA", pt.size = 0.5)
VlnPlot(crypto_CHMI2489_IEL, features = c("nCount_RNA"), pt.size = 0.1) + ylim(0,12000)

VlnPlot(crypto_CHMI2489_IEL, features = c("nFeature_RNA"), pt.size = 0.1) + ylim(0,1000)

length(crypto_CHMI2489_IEL$orig.ident)

crypto_CHMI2489_IEL <- subset(crypto_CHMI2489_IEL, 
                             nFeature_RNA > 150 
                             & nCount_RNA > 250)
```


#CHMI2489_MLN_crypto
```{r}
raw.data <- Read10X(data.dir = "/data/hartandrew/CellRanger/CHMI_183/MIST2489_MLN_crypto/outs/raw_feature_bc_matrix/")
filtered.data <- Read10X(data.dir = "/data/hartandrew/CellRanger/CHMI_183/MIST2489_MLN_crypto/outs/filtered_feature_bc_matrix/")
rownames(x = filtered.data[["Antibody Capture"]]) 
crypto_CHMI2489_MLN <- CreateSeuratObject(counts = filtered.data, project = "crypto_")

FeatureScatter(crypto_CHMI2489_MLN, "nCount_RNA", "nFeature_RNA", pt.size = 0.5)
VlnPlot(crypto_CHMI2489_MLN, features = c("nCount_RNA"), pt.size = 0.1) + ylim(0,12000)

VlnPlot(crypto_CHMI2489_MLN, features = c("nFeature_RNA"), pt.size = 0.1) + ylim(0,1000)

length(crypto_CHMI2489_MLN$orig.ident)

crypto_CHMI2489_MLN <- subset(crypto_CHMI2489_MLN, 
                             nFeature_RNA > 150 
                             & nCount_RNA > 250)


```


#CHMI2493_MLN_crypto
```{r}
raw.data <- Read10X(data.dir = "/data/hartandrew/CellRanger/CHMI_190/MIST2493_MLN_crypto/outs/raw_feature_bc_matrix/")
filtered.data <- Read10X(data.dir = "/data/hartandrew/CellRanger/CHMI_190/MIST2493_MLN_crypto/outs/filtered_feature_bc_matrix/")
rownames(x = filtered.data[["Antibody Capture"]]) 
crypto_CHMI2493_MLN <- CreateSeuratObject(counts = filtered.data, project = "crypto_")

FeatureScatter(crypto_CHMI2493_MLN, "nCount_RNA", "nFeature_RNA", pt.size = 0.5)
VlnPlot(crypto_CHMI2493_MLN, features = c("nCount_RNA"), pt.size = 0.1) + ylim(0,12000)

VlnPlot(crypto_CHMI2493_MLN, features = c("nFeature_RNA"), pt.size = 0.1) + ylim(0,1000)

length(crypto_CHMI2493_MLN$orig.ident)

crypto_CHMI2493_MLN <- subset(crypto_CHMI2493_MLN, 
                             nFeature_RNA > 150 
                             & nCount_RNA > 250)

```


#CHMI2493_LP_crypto
```{r}
raw.data <- Read10X(data.dir = "/data/hartandrew/CellRanger/CHMI_190/MIST2493_LP_crypto/outs/raw_feature_bc_matrix/")
filtered.data <- Read10X(data.dir = "/data/hartandrew/CellRanger/CHMI_190/MIST2493_LP_crypto/outs/filtered_feature_bc_matrix/")
rownames(x = filtered.data[["Antibody Capture"]]) 
crypto_CHMI2493_LP <- CreateSeuratObject(counts = filtered.data, project = "crypto_")

FeatureScatter(crypto_CHMI2493_LP, "nCount_RNA", "nFeature_RNA", pt.size = 0.5)
VlnPlot(crypto_CHMI2493_LP, features = c("nCount_RNA"), pt.size = 0.1) + ylim(0,12000)

VlnPlot(crypto_CHMI2493_LP, features = c("nFeature_RNA"), pt.size = 0.1) + ylim(0,1000)

length(crypto_CHMI2493_LP$orig.ident)

crypto_CHMI2493_LP <- subset(crypto_CHMI2493_LP, 
                             nFeature_RNA > 150 
                             & nCount_RNA > 250)

```

#Can I add crypto infection as a metadata component to this file 

```{r}
head(colnames(crypto_CHMI2489_LP))
#Because of the way they have been merged, the colnames have the orig.ident appended at the beginning. I can manually add this to the crypto alignment so the cell IDs will match
crypto_CHMI2489_LP_names <- colnames(crypto_CHMI2489_LP)
colnames(crypto_CHMI2489_LP) <- paste0("CHMI2489_LP_", crypto_CHMI2489_LP_names)
crypto_CHMI2489_LP_names <- colnames(crypto_CHMI2489_LP)
crypto_CHMI2489_IEL_names <- colnames(crypto_CHMI2489_IEL)
colnames(crypto_CHMI2489_IEL) <- paste0("CHMI2489_IEL_", crypto_CHMI2489_IEL_names)
crypto_CHMI2489_IEL_names <- colnames(crypto_CHMI2489_IEL)

crypto_CHMI2493_LP_names <- colnames(crypto_CHMI2493_LP)
colnames(crypto_CHMI2493_LP) <- paste0("CHMI2493_LP_", crypto_CHMI2493_LP_names)
crypto_CHMI2493_LP_names <- colnames(crypto_CHMI2493_LP)

#crypto_CHMI2493_MLN_names <- colnames(crypto_CHMI2493_MLN)
#colnames(crypto_CHMI2493_MLN) <- paste0("CHMI2493_MLN_", crypto_CHMI2493_MLN_names)
#crypto_CHMI2493_MLN_names <- colnames(crypto_CHMI2493_MLN)

#Find cell IDS which overlap and given them a metadata label of infection
#only 3 samples had cells which pass the filters I created  -- 88 in the 2489 IEL, 18 cells in the 2489 LP and 3 cells in the 2493 LP
infection_vec <- c(crypto_CHMI2489_IEL_names, crypto_CHMI2489_LP_names, crypto_CHMI2493_LP_names)
length(infection_vec)

write.csv(infection_vec, "/data/hartandrew/MIST/SingleCell/Output/cp_infected_cellNames.csv")


```





